Linking assumptions and number of response options modulate inferred scalar implicature rate

### 2018-05-09 writeup.tex
addressed comments

  \usepackage{graphicx}
  \makeatletter
  \def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
  \def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
  \makeatother
  % Scale images if necessary, so that they will not overflow the page
  % margins by default, and it is still possible to overwrite the defaults
  % using explicit options in \includegraphics[width, height, ...]{}
  \setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\ifxetex
  \usepackage[setpagesize=false, % page size defined by xetex
              unicode=false, % unicode breaks when used with xetex
              xetex]{hyperref}
\else
  \usepackage[unicode=true]{hyperref}
\fi
\hypersetup{breaklinks=true,
            pdfauthor={},
            pdftitle={The effect of linking assumptions and number of response options on inferred scalar implicature rate},
            colorlinks=true,
            citecolor=blue,
            urlcolor=blue,
            linkcolor=black,
            pdfborder={0 0 0}}
\urlstyle{same}  % don't use monospace font for urls

@@

% Essential manuscript parts
  \title{The effect of linking assumptions and number of response options on
inferred scalar implicature rate}

@@

The most prominently studied phenomenon in experimental pragmatics is
undoubtedly \emph{scalar implicature}. Scalar implicatures arise in
virtue of a speaker producing the weaker of two ordered scalemates
(hornXXX; {\textbf{???}}, {\textbf{???}}; Grice, 1975). Examples are
provided in (1) and (2).

@@

A listener, upon observing the utterances in (1a) and (2a), typically
infers that the speaker intended to convey the meanings in (1b) and
(2b), respectively. Since Grice (1975), the agreed-upon abstract
rationalization the listener could give for their inference goes
something like this: the speaker could have made a more informative
statement by producing the stronger alternative (e.g., \emph{All of her
pets are cats.}). If the stronger alternative is true, they should have
produced it to comply with the Cooperative Principle. They chose not to.
I believe the speaker knows whether the stronger alternative is true.
Hence, it must not be true.

@@

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  Are scalar inferences default inferences, in the sense that they arise
  unless blocked by (marked) contexts (Degen, 2015; Horn, 1984;
  Levinson, 2000)?
\item
  Are scalar inferences default inferences, in the sense that they are
  computed automatically in online processing and only cancelled by
  context in a second effortful step if required by context) {[}Bott and
  Noveck (2004);Breheny et al. (2006);Degen and Tanenhaus (2016);Grodner
  et al. (2010);Huang and Snedeker (2009);Politzer-Ahles and Fiorentino
  (2013);Tomlinson2013{]}?
\item
  What are the (linguistic and extra-linguistic) factors that affect
  whether a scalar implicature is derived {[}Zondervan (2010);Degen and
  Tanenhaus (2015); Degen and Tanenhaus (2016); Degen (2015); Degen and
  Goodman (2014); Bergen and Grodner (2012); Breheny et al. (2006);
  Breheny, Ferguson, and Katsos (2013);Marneffe and Tonhauser (2016);De
  Neys and Schaeken (2007);Bonnefon, Feeney, and Villejoubert
  (2009);Chemla2011;Potts2015{]}?
\item
  How much diversity is there across implicature types, and within
  scalar implicatures across scale types, in whether or not an
  implicature is computed (Doran, Ward, Larson, McNabb, \& Baker, 2012;
  Tiel, Miltenburg, Zevakhina, \& Geurts, 2014)?
\item
  At what age do children acquire the ability to compute implicatures
  (Barner, Brooks, \& Bale, 2011; Katsos \& Bishop, 2011; Frank;
  Musolino, 2004; Noveck, 2001; Papafragou \& Tantalou, 2004)?
\end{enumerate}

In addressing all of these questions, it has been crucial to obtain
estimates of \textbf{implicature rates}. For 1., implicature rates from
experimental tasks can be taken to inform whether scalar implicatures
should be considered default inferences. For 2., processing measures on
responses that indicate implicatures can be compared to processing
measures on responses that indicate literal interpretations. For 3.,
contextual effects can be examined by comparing implicature rates across
contexts. For 4., implicature rates can be compared across scales (or
across implicature types). For 5., implicature rates can be compared
across age groups.

A standard measure that has stood proxy for implicature rate across many
studies is the proportion of \enquote{pragmatic} judgments in
truth-value judgment paradigms {[}Bott and Noveck (2004);Noveck
(2001);Noveck and Posada (2003);Chemla and Spector (2011);Geurts and
Pouscoulous (2009);Degen and Tanenhaus (2015);De Neys and Schaeken
(2007);Degen2014{]}. In these kinds of tasks, participants are provided
a set of facts, either presented visually or via their own knowledge of
the world. They are then asked to judge whether a sentence intended to
describe those facts is true or false (or alternatively, whether it is
right or wrong, or they are asked whether they agree or disagree with
the sentence). The crucial condition for assessing implicature rates in
these kinds of studies typically consists of a case where the facts are
such that the stronger alternative is true and the target utterance is
thus also true but underinformative. For instance, Bott and Noveck
(2004) asked participants to judge sentences like \enquote{Some
elephants are mammals}, when world knowledge dictates that all elephants
are mammals. Similarly, Degen and Tanenhaus (2015) asked participants to
judge sentences like \enquote{You got some of the gumballs} in
situations where the visual evidence indicated that the participant
received all the gumballs from a gumball machine. In these kinds of
scenarios, the story goes, if a participant responds \enquote{FALSE},
that indicates that they computed a scalar implicature, eg to the effect
of \enquote{Not all elephants are mammals} or \enquote{You didn't get
all of the gumballs}, which is (globally or contextually) false. If
instead a participant responds \enquote{TRUE}, that is taken to indicate
that they interpreted the utterance literally as `Some, and possibly
all, elephants are mammals' or \enquote{You got some, and possibly all,
of the gumballs}.

Given the centrality of the theoretical notion of \enquote{implicature
rate} to much of experimental pragmatics, there is to date a surprising
lack of discussion of the basic assumption that it is adequately
captured by the proportion of FALSE responses in truth-value judgment
tasks (but see ({\textbf{???}}); Geurts and Pouscoulous (2009); Degen
and Goodman (2014); Katsos and Bishop (2011)). Indeed, the scalar
implicature acquisition literature was shaken up when Katsos and Bishop
(2011) showed that simply by introducing an additional response option,
children started looking much more pragmatic than had been previously
observed in a binary judgment paradigm. ({\textbf{???}}) allowed
children to distribute 1, 2, or 3 strawberries to a puppet depending on
\enquote{how good the puppet said it}. The result was that children gave
on average fewer strawberries to the puppet when he produced
underinformative utterances compared to when he produced literally true
and pragmatically felicitous utterances, suggesting that children do, in
fact, display pragmatic ability even at ages when they had previously
appeared not to.

But this raises an important question: in truth-value judgment task, how
do we know whether an interpretation is literal or the result of an
implicature computation? The binary choice task typically used is
appealing in part because it allows for a direct mapping from response
options -- TRUE and FALSE -- to interpretations -- literal and
pragmatic. That the seeming simplicity of this mapping is illusory
becomes apparent once a third response option is introduced, as in the
Katsos and Bishop (2011) case. How is the researcher to interpret the
intermediate option? Katsos and Bishop (2011) grouped the intermediate
option with the negative endpoint of the scale for the purpose of
categorizing judgments as literal vs.~pragmatic. But it seems just as
plausible that they could have grouped it with the positive endpoint of
the scale and taken the hard line that only truly FALSE responses
constitute a full-fledged implicature. The point here is that there has
been remarkably little consideration of \textbf{linking functions}
between behavioral measures and theoretical constructs in experimental
pragmatics, a problem in many subfields of psycholinguistics
({\textbf{???}}). We argue that it is time to engage more seriously with
these issues.

We begin by reporting an experiment that addresses the following
question: do the number of response options provided in a truth-value
judgment task and the way that responses are grouped into pragmatic
(\enquote{SI}) and literal (\enquote{no SI}) change inferences about
scalar implicature rates? Note that this way of asking the question
presupposes two things: first, that whatever participants are doing in a
truth-value judgment task, the behavioral measure can be interpreted as
providing a measure of \textbf{interpretation}. And second, that
listeners either do or do not compute an implicature on any given
occasion. In the Discussion we will discuss both of these issues. First,
following Degen and Goodman (2014), we will offer some remarks on why
truth-value judgment tasks are better thought of as measuring
participants' estimates of speakers' \textbf{production} probabilities.
This will suggest a completely different class of linking functions. And
second, we discuss an alternative conception of scalar implicature as a
probabilistic phenomeonen, a view that has recently rose to prominence
in the subfield of probabilistic pragmatics. This alternative conception
of scalar implicature, we argue, affords developing and testing
quantitative linking functions in a rigorous and motivated way.

Consider a setup in which a listener is presented a card with a
depiction of either one or two animals (see the figure below for an
example). As in a standard truth-value judgment task, the listener then
observes an underinformative utterance about this card (e.g.,
\enquote{There is a cat or a dog on the card}) and is asked to provide a
judgment on a scale from 2 to 5 response options, with endpoints
\enquote{wrong} and \enquote{right}. In the binary case, this reproduces
the standard truth-value judgment task. \textbf{XXX say briefly sth
about wrong/right vs true/false and agree/disagree}. The figure below
exemplifies (some of) the researcher's options for grouping responses.
Under what we will call the \enquote{Strong link} assumption, only the
negative endpoint of the scale is interpreted as evidence for a scalar
implicature having been computed. Under the \enquote{Weak link}
assumption, in contrast, any response that does not correspond to the
positive endpoint of the scale is interpreted as evidence for a scalar
implicature having been computed. Intermediate grouping schemes are also
possible, but these are the ones we will consider here. Note that for
the binary case, the Weak and Strong link return the same categorization
scheme, but for any number of response options greater than 2, the Weak
and Strong link can in principle lead to differences in inferences about
implicature rate.

@@

Let's examine an example. Assume three response options (wrong, neither,
right). Assume further that a third of participants each gave each of
the three responses, i.e., the distributions of responses is 1/3, 1/3,
and 1/3. Under the Strong link, we infer that this task yielded an
implicature rate of 2/3. Under the Weak link, we infer that this task
yielded an implicature rate of 1/3. This is quite a drastic difference
if we are for instance interested in whether scalar implicatures are
inference defaults and we would like to interpret an implicature rate of
above an arbitrary threshold (e.g., 50\%) as evidence for such a claim.
Under the Strong link, we would conclude that scalar implicatures are
not defaults. Under the Weak link, we would conclude that they are.

In the experiment reported in the following section, we presented
participants with exactly this setup. Different groups of participants
were presented with different numbers of response options. We
categorized their responses according to the Weak and the Strong link
and tested whether number of response options and categorization scheme
leads to different conclusions about implicature rates.

@@

@@

200 participants were recruited using Amazon Mechanical Turk (binary=50,
ternary53, quaternary=43, quinary=54). No participant was excluded from
the final analysis.

\subsubsection{Procedure}\label{procedure}

The study was administered online through Amazon Mechanical Turk.
Participants were introduced to a set of cards with pictures of one or
two animals (Figure \ref{fig:stimuli}). They were told that a
blindfolded fictional character called Bob is going to guess what
animals are on the card. On each trial, participants saw a card as well
as a sentence representing Bob's guess. For example, they saw a card
with a cat on it and read the sentence \enquote{There is a cat on the
card.} The study ended after 24 trials. At the end participants
optionally provided demographic information. We also asked participants
if they had any prior training in logic. You can access and view on the
study's \href{https://github.com/thegricean/si-paradigms/}{online
repository}.

\subsubsection{Design and Materials}\label{design-and-materials}

@@

The study had two main manipulaitons within participants: the type of
card and the type of guess. There were two types of cards. Cards with
only one animal on them and cards with two animals. Animals were chosen
from the following set: cat, dog, and elephant There were three types of
guesses: simple (e.g. \emph{There is a cat}), conjunctive (e.g.
\emph{There is a cat and a dog}), and disjunctive (e.g. \emph{There is a
cat or a dog}). In each trial, the animal labels used in the guess and
the animal images on the card may have no overlap (e.g.~Image: cat,
Guess: \emph{There is an elephant}), a partial overlap (e.g.~Image: cat,
Guess: \emph{There is a cat or a dog}), or a total overlap (e.g.~Image:
cat and dog, Guess: \emph{There is a cat or a dog}). Crossing the number
of animals on the card, the type of guess, and the overlap between the
guess and the card results in 12 different possible trial types. We
chose 8 trial types (Figure \ref{fig:trials}), balancing the number of
one-animal vs.~two-animal cards, simple vs.~connective guesses, and
expected true vs.~false trials. Three trials were randomly selected from
each of the 8 trial-types, for a total of 24 trials. The order of these
24 trials was randomized as well.

Participants could derive implicatures in two trial types. First, the
trial type in which two animals were present on the card (e.g.~cat and
dog) but Bob guessed only one of them (e.g. \enquote{there is a cat}).
Such trials can have a literal interpretation (cat and possibly more) or
an exhaustive interpretation (only cat). We refer to them as
\enquote{exhaustive}. The second trial type with implicatures was the
one in which two animals were on the card (e.g.~cat and dog) and Bob
used a disjunciton (e.g.~cat or dog). These trials can have a literal
(inclusive) interpretation (e.g.~cat or dog or both), or an exclusive
interpretation (e.g.~cat or dog, not both). We refer to these trials as
\enquote{scalar}. The following four trial types were used as
experimental control: two trial types where there was no overlap between
the guess (e.g.~elephant) and the animal(s) on the card (e.g.~cat, cat
and dog); and two trial types where the animal(s) on the card were
correctly guessed. For example, if there was only a cat on the card, Bob
said \enquote{there is a cat} and if there was a cat and a dog, Bob said
\enquote{there is a cat and a dog}. Since the fictional character was
blindfolded and did not see the outcome of the game, the ignorance
inference commonly associated with disjunction was already common ground
in the experimental setting. If the character was seeing the cards or
knew what was on them, a disjunction would have violated the expectation
that the speaker does not know which alternative actually holds. Our
study controls for the possibile effect of ignorance violations on
exclusivity and exhaustive inferences.

The study also had a between participant manipulation of the number of
response options in the forced choice task. Participants were randomly
assigned to one of four different conditions. The conditions differed
with respect to the number of response options: binary (wrong
vs.~right), ternary (wrong, neither, right), quaternary (wrong, kinda
wrong, kinda right, right), and quinary (wrong, kinda wrong, neither,
kinda right, right). We wanted to see if the number of response options
in the forced choice task would affect our estimate of the task's
\enquote{implicature rate}.

\begin{figure}
\centering
\includegraphics{writeup_files/figure-latex/trials-1.pdf}
\caption{\label{fig:trials}Trial types represented by example cards and
guesses.}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics{writeup_files/figure-latex/binaryPlot-1.pdf}
\caption{\label{fig:binaryPlot}Proportion responses for the two-alternative
(binary) forced choice judgments in the guessing game.}
\end{figure}

Here we present the proportion that participants chose the response
options in each of the 8 trial types of the binary, ternary, quaternary,
and quinary tasks. Figure \ref{fig:binaryPlot} shows the proportion of
\enquote{right} and \enquote{wrong} responses in the binary task.
Starting from the leftmost column, participants considered a guess
\enquote{wrong} if the guessed animal was not on the card. Moving to the
second column, participants considered a guess \enquote{right} if the
animal on the card was mentioned. However, if only one of the two
animals on the card was mentioned (exhaustive trials), 14\% of the times
participants considered the guess \enquote{wrong}. Moving to the third
column, if a conjunction of animals was guessed while only one animal
was on the card, participants considered the guess to be
\enquote{wrong}. If a conjunction of animals was guessed and both
animals were present on the card, all participants considered the guess
to be \enquote{right} as expected. Moving to the forth column, if a
disjunction of animals was guessed and only one of the animals was on
the card, participants considered the guess to be \enquote{right} almost
all the time. However, if both animals were present (scalar trials),
38\% of the times participants considered the guess to be
\enquote{wrong}.

\begin{figure}
\centering
\includegraphics{writeup_files/figure-latex/ternaryPlot-1.pdf}
\caption{\label{fig:ternaryPlot}Proportion responses for the
three-alternative (ternary) forced choice judgments in the guessing
game.}
\end{figure}

Figure \ref{fig:ternaryPlot} shows the proportion of \enquote{right},
\enquote{neither}, and \enquote{wrong} responses in the ternary task.
Similar to the binary task, participants considered a guess wrong when
the mentioned animal was not on the card. They considered the guess
\enquote{right} when the mentioned animal was on the card. However, in
exhaustive trials when the fictional character only guessed one of the
two animals on the card, participants considered the guess
\enquote{wrong} 8\% of the time and neither wrong nor right 12\% of the
time. If a conjunction of animals was guessed and only one animal was
present on the card, participants considered the guess \enquote{wrong}.
As expected, when a conjunction was used and both animals were present,
participants considered the guess \enquote{right}. Similarly,
participants considerd the guess \enquote{right} when a disjunction was
used and only one of the animals was on the card. However, in scalar
trials that both animals were on the card and a disjunction was
gueassed, participants judged the guess \enquote{wrong} 23\% of the time
and \enquote{neither} 11\% of the time.

\begin{figure}
\centering
\includegraphics{writeup_files/figure-latex/quaternaryPlot-1.pdf}
\caption{\label{fig:quaternaryPlot}Proportion responses for the
four-alternative (quatenary) forced choice judgments in the guessing
game.}
\end{figure}

>>>>

  \usepackage{graphicx}
  \makeatletter
  \def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
  \def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
  \makeatother
  % Scale images if necessary, so that they will not overflow the page
  % margins by default, and it is still possible to overwrite the defaults
  % using explicit options in \includegraphics[width, height, ...]{}
  \setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\ifxetex
  \usepackage[setpagesize=false, % page size defined by xetex
              unicode=false, % unicode breaks when used with xetex
              xetex]{hyperref}
\else
  \usepackage[unicode=true]{hyperref}
\fi
\hypersetup{breaklinks=true,
            pdfauthor={},
            pdftitle={Linking assumptions and number of response options modulate inferred scalar implicature rate},
            colorlinks=true,
            citecolor=blue,
            urlcolor=blue,
            linkcolor=black,
            pdfborder={0 0 0}}
\urlstyle{same}  % don't use monospace font for urls

@@

% Essential manuscript parts
  \title{Linking assumptions and number of response options modulate inferred
scalar implicature rate}

@@

The most prominently studied phenomenon in experimental pragmatics is
undoubtedly \emph{scalar implicature}. Scalar implicatures arise in
virtue of a speaker producing the weaker of two ordered scalemates
(Geurts, 2010; Grice, 1975; Hirschberg, 1985; Horn, 1972). Examples are
provided in (1-2).

@@

A listener, upon observing the utterances in (1-2a) typically infers
that the speaker intended to convey the meanings in (1-2b),
respectively. Since Grice (1975), the agreed-upon abstract
rationalization the listener could give for their inference goes
something like this: the speaker could have made a more informative
statement by producing the stronger alternative (e.g., \emph{All of her
pets are cats.} in (1)). If the stronger alternative is true, they
should have produced it to comply with the Cooperative Principle. They
chose not to. I believe the speaker knows whether the stronger
alternative is true. Hence, it must not be true. The derivation
procedure for ad hoc exhaustive inferences such as in (3) is assumed to
be calculable in the same way as for scalar implicatures, though the
scale is assumed to be contextually driven.

@@

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  Are scalar inferences default inferences, in the sense that they arise
  unless blocked by (marked) contexts (Degen, 2015; Horn, 1984;
  Levinson, 2000)?
\item
  Are scalar inferences default inferences, in the sense that they are
  computed automatically in online processing and only cancelled by
  context in a second effortful step if required by context) (Bott \&
  Noveck, 2004; Breheny et al., 2006; Degen \& Tanenhaus, 2016; Grodner
  et al., 2010; Huang \& Snedeker, 2009; Politzer-Ahles \& Fiorentino,
  2013; Tomlinson, Bailey, \& Bott, 2013)?
\item
  What are the (linguistic and extra-linguistic) factors that affect
  whether a scalar implicature is derived (Bergen \& Grodner, 2012;
  Bonnefon, Feeney, \& Villejoubert, 2009; Breheny, Ferguson, \& Katsos,
  2013; Breheny et al., 2006; Chemla \& Spector, 2011; De Neys \&
  Schaeken, 2007; Degen, 2015; Degen \& Goodman, 2014; Degen \&
  Tanenhaus, 2015, 2016; Marneffe \& Tonhauser, 2016; Potts, Lassiter,
  Levy, \& Frank, 2015; Zondervan, 2010)?
\item
  How much diversity is there across implicature types, and within
  scalar implicatures across scale types, in whether or not an
  implicature is computed (Doran, Ward, Larson, McNabb, \& Baker, 2012;
  Tiel, Miltenburg, Zevakhina, \& Geurts, 2014)?
\item
  At what age do children acquire the ability to compute implicatures
  (Barner, Brooks, \& Bale, 2011; Horowitz, Schneider, \& Frank, 2017;
  Katsos \& Bishop, 2011; Musolino, 2004; Noveck, 2001; Papafragou \&
  Tantalou, 2004; Stiller, Goodman, \& Frank, 2015)?
\end{enumerate}

In addressing all of these questions, it has been crucial to obtain
estimates of \emph{implicature rates}. For 1., implicature rates from
experimental tasks can be taken to inform whether scalar implicatures
should be considered default inferences. For 2., processing measures on
responses that indicate implicatures can be compared to processing
measures on responses that indicate literal interpretations. For 3.,
contextual effects can be examined by comparing implicature rates across
contexts. For 4., implicature rates can be compared across scales (or
across implicature types). For 5., implicature rates can be compared
across age groups.

A standard measure that has stood proxy for implicature rate across many
studies is the proportion of \enquote{pragmatic} judgments in
truth-value judgment paradigms (Bott \& Noveck, 2004; Chemla \& Spector,
2011; De Neys \& Schaeken, 2007; Degen \& Goodman, 2014; Degen \&
Tanenhaus, 2015; Geurts \& Pouscoulous, 2009; Noveck, 2001; Noveck \&
Posada, 2003). In these kinds of tasks, participants are provided a set
of facts, either presented visually or via their own knowledge of the
world. They are then asked to judge whether a sentence intended to
describe those facts is true or false (or alternatively, whether it is
right or wrong, or they are asked whether they agree or disagree with
the sentence). The crucial condition for assessing implicature rates in
these kinds of studies typically consists of a case where the facts are
such that the stronger alternative is true and the target utterance is
thus also true but underinformative. For instance, Bott and Noveck
(2004) asked participants to judge sentences like \enquote{Some
elephants are mammals}, when world knowledge dictates that all elephants
are mammals. Similarly, Degen and Tanenhaus (2015) asked participants to
judge sentences like \enquote{You got some of the gumballs} in
situations where the visual evidence indicated that the participant
received all the gumballs from a gumball machine. In these kinds of
scenarios, the story goes, if a participant responds \enquote{FALSE},
that indicates that they computed a scalar implicature, eg to the effect
of \enquote{Not all elephants are mammals} or \enquote{You didn't get
all of the gumballs}, which is (globally or contextually) false. If
instead a participant responds \enquote{TRUE}, that is taken to indicate
that they interpreted the utterance literally as `Some, and possibly
all, elephants are mammals' or \enquote{You got some, and possibly all,
of the gumballs}.

Given the centrality of the theoretical notion of \enquote{implicature
rate} to much of experimental pragmatics, there is to date a surprising
lack of discussion of the basic assumption that it is adequately
captured by the proportion of FALSE responses in truth-value judgment
tasks (but see Benz and Gotzner (2014); Geurts and Pouscoulous (2009);
Degen and Goodman (2014); Katsos and Bishop (2011)). Indeed, the scalar
implicature acquisition literature was shaken up when Katsos and Bishop
(2011) showed that simply by introducing an additional response option,
children started looking much more pragmatic than had been previously
observed in a binary judgment paradigm. Katsos and Bishop (2011) allowed
children to distribute 1, 2, or 3 strawberries to a puppet depending on
\enquote{how good the puppet said it}. The result was that children gave
on average fewer strawberries to the puppet when he produced
underinformative utterances compared to when he produced literally true
and pragmatically felicitous utterances, suggesting that children do, in
fact, display pragmatic ability even at ages when they had previously
appeared not to.

But this raises an important question: in truth-value judgment tasks,
how does the researcher know whether an interpretation is literal or the
result of an implicature computation? The binary choice task typically
used is appealing in part because it allows for a direct mapping from
response options -- TRUE and FALSE -- to interpretations -- literal and
pragmatic. That the seeming simplicity of this mapping is illusory
becomes apparent once a third response option is introduced, as in the
Katsos and Bishop (2011) case. How is the researcher to interpret the
intermediate option? Katsos and Bishop (2011) grouped the intermediate
option with the negative endpoint of the scale for the purpose of
categorizing judgments as literal vs.~pragmatic, i.e., they interpreted
the intermediate option as pragmatic. But it seems just as plausible
that they could have grouped it with the positive endpoint of the scale
and taken the hard line that only truly FALSE responses constitute
evidence of a full-fledged implicature. The point here is that there has
been remarkably little consideration of \emph{linking functions} between
behavioral measures and theoretical constructs in experimental
pragmatics, a problem in many subfields of psycholinguistics (Tanenhaus,
2004). We argue that it is time to engage more seriously with these
issues.

We begin by reporting an experiment that addresses the following
question: do the number of response options provided in a truth-value
judgment task and the way that responses are grouped into pragmatic
(\enquote{SI}) and literal (\enquote{no SI}) change inferences about
scalar implicature rates? Note that this way of asking the question
presupposes two things: first, that whatever participants are doing in a
truth-value judgment task, the behavioral measure can be interpreted as
providing a measure of \emph{interpretation}. And second, that listeners
either do or do not compute an implicature on any given occasion. In the
General Discussion we will discuss both of these issues. First,
following Degen and Goodman (2014), we will offer some remarks on why
truth-value judgment tasks are better thought of as measuring
participants' estimates of speakers' \emph{production} probabilities.
This will suggest a completely different class of linking functions. And
second, we discuss an alternative conception of scalar implicature as a
probabilistic phenomeonen, a view that has recently rose to prominence
in the subfield of probabilistic pragmatics (Franke \& Jäger, 2016;
Goodman \& Frank, 2016). This alternative conception of scalar
implicature, we argue, affords developing and testing quantitative
linking functions in a rigorous and motivated way.

Consider a setup in which a listener is presented a card with a
depiction of either one or two animals (see Figure
\ref{fig:linkvisualization} for an example). As in a standard
truth-value judgment task, the listener then observes an
underinformative utterance about this card (e.g., \enquote{There is a
cat or a dog on the card}) and is asked to provide a judgment on a scale
with 2, 3, 4, or 5 response options, with endpoints \enquote{wrong} and
\enquote{right.}\footnote{An open question concerns the extent to which
  the labeling of points on the scale affects judgments (e.g.,
  \enquote{wrong}--\enquote{right} vs. \enquote{false}--\enquote{true}
  vs. \enquote{disagree}--\enquote{agree}). While some studies have used
  \enquote{false}--\enquote{true}, others have argued that judging truth
  may lead to meta-linguistic reasoning in participants that could
  distort judgments.} In the binary case, this reproduces the standard
truth-value judgment task. Figure \ref{fig:linkvisualization}
exemplifies (some of) the researcher's options for grouping responses.
Under what we will call the \enquote{Strong link} assumption, only the
negative endpoint of the scale is interpreted as evidence for a scalar
implicature having been computed. Under the \enquote{Weak link}
assumption, in contrast, any response that does not correspond to the
positive endpoint of the scale is interpreted as evidence for a scalar
implicature having been computed. Intermediate grouping schemes are also
possible, but these are the ones we will consider here. Note that for
the binary case, the Weak and Strong link return the same categorization
scheme, but for any number of response options greater than 2, the Weak
and Strong link can in principle lead to differences in inferences about
implicature rate.

@@

Let's examine an example. Assume three response options (wrong, neither,
right). Assume further that a third of participants each gave each of
the three responses, i.e., the distributions of responses is 1/3, 1/3,
and 1/3. Under the Strong link, we infer that this task yielded an
implicature rate of 2/3. Under the Weak link, we infer that this task
yielded an implicature rate of 1/3. This is quite a drastic difference
if we are for instance interested in whether scalar implicatures are
inference defaults and we would like to interpret an implicature rate of
above an arbitrary threshold (e.g., 50\%) as evidence for such a claim.
Under the Strong link, we would conclude that scalar implicatures are
not defaults. Under the Weak link, we would conclude that they are. In
the experiment reported in the following section, we presented
participants with exactly this setup. We manipulated the number of
response options between participants and analyzed the results under
different linking assumptions.

@@

Participants played an online card game in which they were asked to
judge descriptions of the contents of cards. Different groups of
participants were presented with different numbers of response options.
On critical trials, participants were presented with descriptions for
the cards that typically result in exhaustivity implicatures
(\enquote{There is a cat on the card} when there was a cat and a dog) or
scalar implicatures (\enquote{There is a cat or a dog on the card} when
there was a cat and a dog). We categorized their responses on such
trials according to the weak and the strong link introduced above, and
tested whether the number of response options and the linking
assumptions led to different conclusions about the rate of computed
implicatures in the experimental task.

@@

200 participants were recruited via Amazon Mechanical Turk. They
optionally provided demographic information at the end of the study.
Participants' mean age was 35. We also asked participants if they had
any prior training in logic. 40 participants reported that they did,
while 160 had no prior training in logic. \textbf{JD: Do we do any
analysis of logic training???} All participants' data was included in
the final analysis.

\subsubsection{Materials and procedure}\label{materials-and-procedure}

The study was administered online through Amazon Mechanical
Turk.\footnote{The experiment can be viewed
  \href{https://cdn.rawgit.com/thegricean/si-paradigms/94a590f0/experiments/main/1_methods/online_experiment/connective_game.html}{here}.}
Participants were first introduced to the set of cards we used in the
study (Figure \ref{fig:stimuli}). Each card depicted one or two animals,
where an animal could be either a cat, a dog, or an elephant. Then
participants were introduced to a blindfolded fictional character called
Bob. Bob was blindfolded to avoid violations of ignorance expectations
associated with the use of disjunction ({\textbf{???}}; Chierchia et
al., 2001) \textbf{JD: Masoud, can you insert citation pls? Geurts,
Sauerland?}. Participants were told that Bob would guess the contents of
the cards and their task was to indicate whether Bob's guess was wrong
or right. On each trial, participants saw a card and a sentence
representing Bob's guess. For example, they saw a card with a cat and
read the sentence \enquote{There is a cat on the card.} They then
provided an assessment of Bob's guess. The study ended after 24 trials.

@@

Two factors were manipulated within participants: card type and guess
type. There were two types of cards, cards with only one animal on them
and cards with two animals. There were three types of guesses: simple
(e.g. \emph{There is a cat}), conjunctive (e.g. \emph{There is a cat and
a dog}), and disjunctive (e.g. \emph{There is a cat or a dog}). Crossing
card type and guess type yielded trials of varying theoretical interest
(see Figure \ref{fig:trials}): critical underinformative trials that
were likely to elicit pragmatic inferences (either scalar or exhaustive)
and control trials that were either unambiguously true or false. Each
trial type occurred three times with randomly sampled animals and
utterances that satisfied the constraint of the trial type. Trial order
was randomized.

\begin{figure}
\centering
\includegraphics{writeup_files/figure-latex/trials-1.pdf}
\caption{\label{fig:trials}Trial types (critical and control). Headers
indicate utterance types. Rows indicate card types. Critical trials are
marked in bold.}
\end{figure}

On critical trials, participants could derive implicatures in two ways.
First, on trials on which two animals were present on the card (e.g.,
cat and dog) but Bob guessed only one of them (e.g. \enquote{There is a
cat on the card}), the utterance could have a literal interpretation
(\enquote{There is a cat and possibly another animal on the card}) or an
exhaustive interpretation (\enquote{There is only a cat on the card}).
We refer to these trials as \enquote{exhaustive}. Second, on trials on
which two animals were on the card (e.g., a cat and a dog) and Bob used
a disjunciton (e.g., \enquote{There is a cat or a dog on the card}), the
utterance could have the literal, inclusive, interpretation, or a
pragmatic, exclusive interpretation. We refer to these trials as
\enquote{scalar}.

In order to assess the effect of the number of response options on
implicature rate, we manipulated number of response options in the
forced choice task between participants. We refer to the choice
conditions as \enquote{binary} (options: \emph{wrong}, \emph{right}),
\enquote{ternary} (options: \emph{wrong}, \emph{neither}, \emph{right}),
\enquote{quaternary} (options: \emph{wrong}, \emph{kinda wrong},
\emph{kinda right}, \emph{right}), and \enquote{quinary} (\emph{wrong},
\emph{kinda wrong}, \emph{neither}, \emph{kinda right}, \emph{right}).
Thus, the endpoint labels always remained the same. If there was an
uneven number of response options, the central option was
\emph{neither}. Participants were randomly assigned to one of the four
task conditions.

@@

The collected dataset contains 50 participants in the binary task, 53 in
the ternary task, 43 in the quaternary task, and 54 in the quinary task.
Figures \ref{fig:binaryPlot} to \ref{fig:quinaryPlot} show the
proportions of response choices in each of the 8 trial types on each of
the four response tasks, respectively. We report the relevant patterns
of results qualitatively before turning to the quantitative analysis of
interest.

\subsubsection{Qualitative analysis}\label{qualitative-analysis}

\begin{figure}
\centering
\includegraphics{writeup_files/figure-latex/binaryPlot-1.pdf}
\caption{\label{fig:binaryPlot}Proportion of responses for the binary forced
choice judgments. Error bars indicate 95\% bootstrapped confidence
intervals.}
\end{figure}

In the binary task, participants were at or close to ceiling in
responding \enquote{right} and \enquote{wrong} on unambiguously true and
false trials, respectively (see Figure \ref{fig:binaryPlot}). However,
on underinformative trials (\enquote{cat} and \enquote{cat or dog}
description for card with cat and dog), we observe pragmatic behavior:
on exhaustive trials, participants judged the utterance \enquote{wrong}
14\% of the time; on scalar trials, participants judged the utterance
\enquote{wrong} 38\% of the time. That is, both under the weak and the
strong link assumptions introduced in the Introduction, inferred
implicature rate on exhaustive trials is 14\% and on scalar trials 38\%.

\begin{figure}
\centering
\includegraphics{writeup_files/figure-latex/ternaryPlot-1.pdf}
\caption{\label{fig:ternaryPlot}Proportion of responses for the ternary
forced choice judgments. Error bars indicate 95\% bootstrapped
confidence intervals.}
\end{figure}

In the ternary task, participants were also at or close to ceiling in
responding \enquote{right} and \enquote{wrong} on unambiguously true and
false trials, respectively (see Figure \ref{fig:ternaryPlot}). And
again, on underinformative trials (\enquote{cat} and \enquote{cat or
dog} description for card with cat and dog), we observed pragmatic
behavior: on exhaustive trials, participants considered the guess
\enquote{wrong} 8\% of the time and neither wrong nor right 12\% of the
time. On scalar trials, participants judged the guess \enquote{wrong}
23\% of the time and \enquote{neither} 11\% of the time. This means that
the weak and strong link lead to different conclusions about implicature
rates on the ternary task. Under the weak link, inferred implicature
rate on exhaustive trials is 20\%; under the strong link it is only 8\%.
Similarly, under the weak link, inferred implicature rate on scalar
trials is 34\%; under the strong link it is only 23\%.

\begin{figure}
\centering
\includegraphics{writeup_files/figure-latex/quaternaryPlot-1.pdf}
\caption{\label{fig:quaternaryPlot}Proportion of responses for the
quaternary forced choice judgments. Error bars indicate 95\%
bootstrapped confidence intervals.}
\end{figure}
